---
World Dataset 2023
---

```{r}
install.packages('tidyverse')
library(tidyverse)

```

---

---

```{r}
df <- read_csv("C:/Users/aniru/OneDrive/Documents/codingtemple/week8/world-data-2023.csv")
df
```

```{r}
df1<- df[-c(3,8:11,12:16,21,23,25:27,29, 31,33:35)]
```

```{r}
df1
```

```{r}
colnames(df1) <- c('country','density ','agricultural_land','land_area','armed_forces_size','birth_rate','gdp','gross_primary_ education_enrollment','gross_tertiary_education_enrollment','infant_mortality','life_expectancy','minimum_wage','population','tax_revenue','unemployment_rate')
```

```{r}

df1
```

```{r}
colSums(is.na(df1))
```

```{r}
sum(colSums(is.na(df1)))
```

```{r}
df1 <- df1 %>% 
    mutate_if(is.numeric, ~replace_na(., 0))
```

```{r}
df1
```

```{r}
colSums(is.na(df1))
```

```{r}
df1

```

```{r}
df1 %>% 
    arrange(desc(life_expectancy)) %>%
    slice(1:10) %>%
    ggplot(. ,aes(country, life_expectancy))+
geom_point()
```

```{r}
df1 %>% 
    arrange(desc(armed_forces_size)) %>%
    slice(1:10) %>%
    ggplot(. ,aes(country, armed_forces_size))+
geom_point()
```

```{r}
df1 %>% 
    arrange(desc(unemployment_rate)) %>%
    slice(1:10) %>%
    ggplot(. ,aes(country, unemployment_rate))+
geom_point()
```

```{r}
df1 %>% 
    arrange(desc(population)) %>%
    slice(1:10) %>%
    ggplot(. ,aes(country, population))+
geom_point()
```

```{r}
write.csv(df1, "world_data_2023.csv")
```

```{r}
ggplot(data = df1) +
  geom_point(mapping = aes(x =life_expectancy , y = infant_mortality))
```

```{r}
ggplot(data = df1) +
  geom_point(mapping = aes(x =birth_rate , y = infant_mortality))
```

```{r}
df2 <- select_if(df1, is.numeric) 
summary(df2)
```

```{r}
result = cor.test(df1$infant_mortality, df1$birth_rate)
result
```

---
p value is 2.2e-16
r value or correlation coefficient value is 0.8583599 
This means the p-value is a lot less than 0.05, which means we can reject the null hypothesis that β = 0. Hence, there is a significant relationship between the variables
+.70 or higher - Very strong positive relationship or correlation
---

```{r}
result1 = cor.test(df1$birth_rate, df1$life_expectancy)
result1
```

---
This means we retain the null hypothesis and reject the alternative hypothesis as p - value is greater than 0.05.
	No or negligible relationship because correlation coefficient is -0.0512559 
---

```{r}
result2 = cor.test(df1$population, df1$armed_forces_size)
result2
```

---
p value is 2.2e-16
r value or correlation coefficient value is 0.8583599 
This means the p-value is a lot less than 0.05, which means we can reject the null hypothesis that β = 0. Hence, there is a significant relationship between the variables
+.70 or higher - Very strong positive relationship or correlation
---

```{r}
```

```{r}

  
```

```{r}

```
